SunPy - Python for Solar Physics

### 2014-01-24 2-Data_Types.tex
Some edits to datatypes

\section{Core Data Types}
One of the primary focus' of the SunPy library is to provide data structures 
that are specifically designed for the various types of data generally 
processed for solar physics. Currently SunPy provides three data 
types, each separate from one another to process 2D spatial data 
(\texttt{Map}), 1D temporal series (\texttt{LightCurve}) and 1 and 2D spectra 
(\texttt{Spectrum} and \texttt{Spectra}).

The design of SunPy's core data types is as a wrapper around a data object, 
either a \texttt{numpy} \texttt{ndarray} or a \texttt{pandas} 
\texttt{DataFrame}, for \texttt{Map} and \texttt{Spectra} and 
\texttt{LightCurve} respectively. Each data type has a \texttt{.data} 
attribute where this data object is located and some meta data. It is 
possible to instantiate the data types from various different 
sources, \textit{e.g.} files, urls, arrays or time ranges. The 
specific sources supported is dependant upon which data type and 
which instrument. All the SunPy data types support specialisation on 
a per-instrument basis, \textit{i.e.} \texttt{Map} has a 
\texttt{AIAMap} sub-type. This design allows simple extensions to 
cope with the diversity of data from different sources in solar 
physics. As well as support for different instruments and data 
sources each data type supports different visualisation wrappers that 
allow both quick view plotting (the peek command) and more 
fine-grained control plotting that integrates well with 
\texttt{matplotlib} (the plot command).

>>>>

\section{Core Data Types}
One of the primary focus' of the SunPy library is to provide data structures 
that are specifically designed for the various types of data generally 
processed for solar physics. Currently SunPy provides three data 
types, each separate from one another to process 2D spatial data 
(\texttt{Map}), 1D temporal series (\texttt{LightCurve}) and 1 and 2D spectra 
(\texttt{Spectrum} and \texttt{Spectrogram}).

The design of SunPy's core data types is as a wrapper around a data object, 
either a \texttt{numpy} \texttt{ndarray} -- for \texttt{Map} and \texttt{Spectra} -- or a \texttt{pandas} \texttt{DataFrame} -- for \texttt{LightCurve}.
 Each data type has a \texttt{.data} 
attribute where this data object is located and some meta data. It is 
possible to instantiate the data types from various different 
sources, \textit{e.g.} files, urls, arrays or time ranges. The 
specific sources supported is dependant upon which data type and 
which instrument. All the SunPy data types support specialisation on 
a per-instrument basis, \textit{i.e.} \texttt{Map} has an 
\texttt{AIAMap} sub-type. This design allows simple extensions to 
cope with the diversity of data from different sources in solar 
physics. As well as support for different instruments and data 
sources each data type provides different visualisation wrappers that 
allow both quick view plotting (the peek command) and more 
fine-grained control plotting that integrates well with 
\texttt{matplotlib} (the plot command).
